Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-26 outputs/paper/paper.qmd
fine-tune writing and finalize paper

The data package used for analysis was sourced from the Open Data Toronto Portal under the library `opendatatoronto` [@rOpenDataToronto]. Only one dataset was retrieved from the data package to examine the racial and gender identities of Toronto police arrests from 2020 to 2021, which is the package `Police Race and Identity Based Data - Arrests and Strip Searches` [@torontoPolice]. Data was generated, extracted and cleaned using the open-source statistical programming language R [@r], leveraging functions from `tidyverse` [@rTidyverse], `ggplot2` [@rGgplot2], `dplyr` [@rDplyr], `readr` [@rReadr], `tibble` [@rTibble], `here` [@rHere], `ggrepel` [@rGgrepel], janitor` [@rJanitor], `kableExtra` [@rKableExtra], `naniar` [@rNaniar] and `knitr` [@rKnitr].

>>>>

The data package used for analysis was sourced from the Open Data Toronto Portal under the library `opendatatoronto` [@rOpenDataToronto]. Only one dataset was retrieved from the data package to examine the racial and gender identities of Toronto police arrests from 2020 to 2021, which is the package `Police Race and Identity Based Data - Arrests and Strip Searches` [@torontoPolice]. Data was generated, extracted and cleaned using the open-source statistical programming language R [@r], leveraging functions from `tidyverse` [@rTidyverse], `ggplot2` [@rGgplot2], `dplyr` [@rDplyr], `readr` [@rReadr], `tibble` [@rTibble], `here` [@rHere], `ggrepel` [@rGgrepel], `janitor` [@rJanitor], `kableExtra` [@rKableExtra], `naniar` [@rNaniar], and `knitr` [@rKnitr].
